\documentclass[12pt,twoside,a4paper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[super]{nth}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\expHeading}[3]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}, \textit{\small#2} & #3
    \end{tabular*}\vspace{-15pt}
}

\newcommand{\expSubHeading}[2]{
  \vspace{0pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-15pt}
}

\newcommand{\expTechUsed}[1]{
  \vspace{0pt}
  \textbf{Technologies}: {#1}
  \vspace{0pt}
}

\newcommand{\expDescription}[1]{
  \vspace{0pt}
  \textbf{Responsibilities}: {#1}
  \vspace{0pt}
}

\newcommand{\expProject}[1]{
  \vspace{0pt}
  \textbf{Projects}: {#1}
  \vspace{6pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}
{\textwidth}
{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Hao Wooi Lim, Simon}} & Email: \href{mailto:zybler@gmail.com}{zybler@gmail.com}\\
  {LinkedIn: \href{https://www.linkedin.com/in/haowooilim/}{linkedin.com/in/haowooilim}} & Mobile: +61 4 3433 8642 \\
  {Github: \href{https://www.github.com/azybler/}{github.com/azybler}} & Visa: Singapore PR, TSS 482
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tunku Abdul Rahman University (UTAR)}{Petaling Jaya, Malaysia}
      {Bachelor of Information Technology (Hons) Computer Engineering}{May 2005 -- May 2008}

    \resumeSubheading
      {Tunku Abdul Rahman College (KTAR)}{Setapak, Malaysia}
      {Diploma in Science (Information Systems Engineering)}{Mar. 2004 -- Mar. 2005}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \expHeading
      {Nine}{Sydney, Australia}{Sep. 2021 -- Now}

    \expSubHeading
      {Software Engineer (Backend)}{Sep. 2021 -- Now}

    \expTechUsed
      {Golang, GraphQL, React JS, TypeScript, Kubernetes, SQS, Postgres}

    \expDescription
      {
        \begin{enumerate}
          \item Developed/maintained Nine's new election backend system \& election widgets to replace a legacy election system with a more modern infra to better handle increased user traffic \& improved UX.
          \item Written scripts \& performed data migration from legacy CQ system to Nine's current backend as part of an effort to deprecate legacy systems.
          \item Developed/maintained Nine's Good Food \& Traveller sub-brand web site.
          \item Performed on-call duties to investigate production issues \& timely deployment of features.
          \item Performed code review \& peer-testing to ensure the team's work are of high standard.
        \end{enumerate}
      }

    \expHeading
      {Canva}{Sydney, Australia}{Jan. 2021 -- Sep 2021 (8 months)}

    \expSubHeading
      {Software Engineer (Backend)}{Jan. 2021 -- Sep 2021 (8 months)}

    \expTechUsed
      {Java, DynamoDB, Terraform, React JS, AWS, MySQL}

    \expDescription
      {
        \begin{enumerate}
          \item Developed/maintained Canva's folder backend to improve stability \& support new business requirements.
          \item Designed/developed as part of a team of 3 to migrate all documents to a new data scheme to support a new View called "Your Projects".
          \item Migrated legacy folder APIs from reading/writing to MySQL to DynamoDB as part of effort to modernize the data backend \& better handle increased user traffic. \& 
          \item Performed on-call duties to investigate production issues \& responds to customer tickets.
          \item Performed code review to ensure the team's work are of high standard.
        \end{enumerate}
      }

    \expDescription
      {Developed/maintained Canva's Content management system.}

    \expHeading
      {Grab}{Singapore}{Jul. 2014 -- Sep. 2020 (6 years, 2 months)}

    \expSubHeading
      {Senior Backend Engineer}{Jul. 2018 -- Sep. 2020 (2 years, 2 months)}

    \expTechUsed
      {Golang, Redis, JavaScript, AWS, Terraform, SQS}

    \expDescription
      {
        \begin{enumerate}
          \item Spearheaded \& coordinated efforts to develop Snap-to-Road v3 to replace current Snap to Road system to enable real-time snapping of raw driver GPS location. System is launched with 41\% reduction in latency (12ms to 7ms) \& 60\% reduction in AWS infra cost.
          \item Developed/maintained a multi-modal route planner based on the "Connection Scan Algorithm" to enable route planning functionality on app.
          \item Developed internal visualization tools to help diagnose tricky Snap-to-Road failures.
          \item Performed on-call duties to investigate production issues \& responds to customer tickets.
          \item Performed code review to ensure the team's work are of high standard.
        \end{enumerate}
      }

    \expSubHeading
      {Senior Full Stack Developer}{Jan. 2016 -- Jun. 2018 (2 years, 6 months)}

    \expTechUsed
      {Ruby on Rails, React JS, AWS, MySQL}

    \expDescription
      {Developed/maintained Grab's various internal \& public-facing web apps, e.g. Driver Onboarding Platform, Share My Ride, \href{https://business.grab.com/}{Grab for Business}, FlagsView using technologies like \href{https://rubyonrails.org/}{Ruby on Rails}, JavaScript, \href{https://reactjs.org/}{ReactJS}, \href{https://graphql.org/}{GraphQL} \& \href{https://www.mysql.com/}{MySQL}.}

    \expSubHeading
      {Senior Node.js Developer}{Jul. 2014 -- Jun. 2014 (1 year, 6 months)}

    \expTechUsed
      {Node.JS, AWS, MySQL}

      \expDescription
        {Developed/maintained Dispatcher (one of the early core systems of Grab, responsible for notification, bidding \& acceptance of all rides). Technologies like \href{https://nodejs.org/}{Node.js}, \href{https://www.mysql.com/}{MySQL} is used.}

    \expHeading
      {YellowElevator}{Malaysia}{Jan. 2014 -- Jun. 2014 (6 months)}

    \expSubHeading
      {Senior Software Developer}{}

      \expDescription
        {Developed/maintained YellowElevator web site. Dabble with \href{https://www.php.net/}{php} using \href{https://framework.zend.com/}{Zend Framework} \& \href{https://www.mysql.com/}{MySQL} for the database, JQuery \& some vanilla JavaScript on the frontend. Worked on the site's Notifications Center. Also helped in requirement analysis \& architecture design.}

    \expHeading
      {Time.ly, GuideAdvisor}{Contract/Remote}{Apr. 2013 -- Oct. 2013 (7 months)}

    \expSubHeading
      {Software Developer}{}

      \expDescription
        {Developed/maintained a popular calendar widget for wordpress called timely \& GuideAdvisor site. Developed backend \href{https://nodejs.org/}{Node.js}-based API router that is covered by BDD test written with vows. Worked on features like filtering (selectize, select2), automatic layout (Masonry), infinite scrolling.}

    \expHeading
      {EzyPay}{Malaysia}{Jul. 2011 -- Jan. 2013 (1 year, 7 months)}

    \expSubHeading
      {Senior Developer}{}

      \expDescription
        {Helped in development/maintenance of iConnect360 Silverlight application. Dabbling with C\# \& .NET 4.5, Telerik RadControls for Silverlight. Worked on the site's new Booking management module \& E-mail campaign management module. Software Development is done via true Scrum methodologies. Heavily involved in requirement analysis \& planning/estimation.}

    \expHeading
      {Panasonic R\&D Centre Malaysia}{Malaysia}{Jun. 2008 -- Jun. 2009 (1 year, 1 months)}

    \expSubHeading
      {Research \& Development Engineer}{}

      \expDescription
        {Developed software that manages Panasonic's various PBX system using the Qt library \& C\#. Tasked to understand existing large C++ codebase \& fix bugs in existing software, performed testing on software that sometimes require interfacing with hardware \& add new functionality according to hardware specifications.}

  \resumeSubHeadingListEnd

% --------PAST & CURRENT PROJECTS------------
\section{Past \& Current Projects}
 \resumeSubHeadingListStart
   \item{
     \textbf{Snap-to-Road (Grab)}{: This is a microservice to accurately position drivers. It’s built with \href{https://golang.org/}{Go} \& \href{https://redis.io/}{Redis} as the data store. Known as “\href{https://en.wikipedia.org/wiki/Map_matching}{map matching}” in the research community, our approach uses the hidden Markov model. Initial implementation is adapted from the paper “Hidden Markov Map Matching Through Noise \& Sparseness”. As the initial author of Snap-to-Road V3, I’m involved in the initiation \& planning phase \& has successfully brought it to production. V3 has novel aspects not documented in the paper that enables real-time snapping that will be documented in a patent pending submission where I’m also one of the core authors. I also helped to reduce infra costs by means of code optimization (e.g. making use of Sync Pool) \& revising ASG policies via \href{https://www.terraform.io/}{Terraform}.}
   }
   \item{
     \textbf{Multi-modal route planner (Grab)}{: This is a microservice to suggest best routing plan across various modalities, e.g. Trains, Buses and/or Grab rides. Its approach is based on the paper “Connection Scan Algorithm”. Form an initial implementation by a fellow team member, I worked on getting it production-ready, fixed critical bugs, added tests \& built visualization tools for correctness verification.}
   }
   \item{
     \textbf{\href{https://business.grab.com/}{Grab for Business}}{: Consisting of a web portal, admin portal, revamp of Grab’s passenger app \& various other integration work with the rest of Grab internal systems. The system as a whole allows businesses to manage ride policies, payment methods \& employees. Employees of enrolled businesses will be able to take corporate rides in accordance to the company’s pre-set policies.}
   }
   \item{
     \textbf{Driver Onboarding (Grab)}{: Consisting of a web portal, admin portal, it is a system designed to improve the experience of signing up, vetting \& onboarding drivers. The sign up form is designed with \href{https://reactjs.org/}{ReactJS} \& optimized to load fast \& responsive even on low-end smartphones.}
   }
   \item{
     \textbf{Dispatcher (Grab)}{: This is one of the major backend systems used for sending/receiving of messages to/from driver such as a job broadcast to driver \& handling of bidding/cancelling etc. It broadcast jobs to driver using a persistent TCP connection to the driver. It is written using \href{https://nodejs.org/}{Node.js}. It initially uses the async library for control flow. I worked on the transition to use node-sync. I also worked on the separation of dispatcher into communication layer \& logic layer to achieve graceful restart that avoids the disconnection of every driver during every deployment.}
   }
   \item{
     \textbf{Rotation-invariant License Plate Detector (Final year project)}{: This is a license plate detector developed with Pedro F. Felzenszwalb \& Daniel P. Huttenlocher's graph-based image segmentation algorithm (their algorithm is open source but I have to port it over to use OpenCV). It uses variance-based features \& is integrated with libsvm. It is written in C++ with OpenCV. The algorithm does not achieve groundbreaking results compared to existing solutions, but it was a novel method \& provides the basis for future Computer-Vision related research.)}
   }
 \resumeSubHeadingListEnd

% --------AWARDS------------
\section{Awards}
 \resumeSubHeadingListStart
   \item{
     \textbf{The Rookie Award 2011}{\\Awarded for being the best overall new comer of the quarter (as voted by working colleagues in EzyPay.}
   }
   \item{
     \textbf{The Exterminator Award 2011}{\\Awarded for being the best bug fixer of the quarter (as voted by working colleagues in EzyPay.}
   }
   \item{
     \textbf{Bitwise 2009 Online Algorithm Programming Contest}{\\Placed \nth{33} among 2700 teams from around the world.}
   }
   \item{
     \textbf{Microsoft Imagine Cup 2008 – Software Design}{\\Placed \nth{2} among 5 teams in the Malaysia finals.}
   }
   \item{
     \textbf{Bitwise 2008 Online Algorithm Programming Contest}{\\Placed \nth{24} among 2911 teams from around the world.}
   }
   \item{
     \textbf{PanaGEEK 2007 programming competition}{\\Top 20 in the national first round, \nth{3} prize in the final round.}
   }
 \resumeSubHeadingListEnd

% --------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Stacks}{: \href{https://rubyonrails.org/}{Ruby on Rails}, \href{https://reactjs.org/}{ReactJS}, \href{https://nodejs.org/}{Node.js}, \href{https://graphql.org/}{GraphQL}, \href{https://framework.zend.com/}{Zend Framework}, \href{https://www.terraform.io/}{Terraform}}
   }
   \item{
     \textbf{Databases}{: \href{https://www.mysql.com/}{MySQL}, \href{https://redis.io/}{Redis}}
   }
   \item{
     \textbf{Languages}{: \href{https://golang.org/}{Go}, JavaScript, C/C++, \href{https://www.php.net/}{PHP}, C\#, Java, \href{https://www.rust-lang.org/}{Rust}, Ruby, SQL}
   }
   \item{
     \textbf{Methodologies}{: Scrum, Kanban, Agile}
   }
 \resumeSubHeadingListEnd

% --------PUBLICATIONS------------
\section{Publications}
 \resumeSubHeadingListStart
   \item{
     {Visual Objects Classification with Sliding Spatial Pyramid Matching, 2012}{\\\textit{\href{https://arxiv.org/abs/1212.3767}{arxiv.org/abs/1212.3767}}}
   }
   \item{
     {Detection of License Plate Characters in Natural Scene with MSER and SIFT unigram Classifier, 2010}{\\\textit{\href{https://ieeexplore.ieee.org/document/5686998}{ieeexplore.ieee.org/document/5686998}}}
   }
   \item{
     {Vehicle License Plate Detection using Unigram Model and Difference-of-SURF Bigram Model with SVM, 2009}{\\\textit{\href{https://www.semanticscholar.org/paper/PLATE-DETECTION-USING-UNIGRAM-MODEL-AND-BIGRAM-WITH-Lim-Tay/fd81d1a75e49c0e96c57ec2a64a259ee22af99fc}{semanticscholar.org/paper/PLATE-DETECTION-USING-UNIGRAM-MODEL-AND-BIGRAM-WITH-Lim-Tay/fd81d1a75e49c0e96c57ec2a64a259ee22af99fc}}}
   }
   \item{
     {Two-stage License Plate Detection using Gentle Adaboost and SIFT-SVM, 2009}{\\\textit{\href{https://ieeexplore.ieee.org/document/5175977}{ieeexplore.ieee.org/document/5175977}}}
   }
   \item{
     {Fast Adaptive Graph-based Segmentation with application in Vehicle License Plate Detection, 2008}{\\\textit{\href{https://www.semanticscholar.org/paper/Fast-Adaptive-Graph-based-Segmentation-with-in-Lim-Tay/6f0128a7630687189a9fdcafd15111f8e461ebb0}{semanticscholar.org/paper/Fast-Adaptive-Graph-based-Segmentation-with-in-Lim-Tay/6f0128a7630687189a9fdcafd15111f8e461ebb0}}}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
